\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{Sawaiz Syed}

\section{Work experience}

\begin{eventlist}

\item{January 2014 -- Present}
     {Georgia State University, Atlanta, GA}
     {Hardware Developer}
     
Design wireless Geiger counter mesh for production. Layout and testing of
schematics and PCB. Software development using C, C++. Create 
documentation for future users and development.

\item{December 2013 -- Feburary 2014}
     {Fry's Electronics, Alpharetta, GA}
     {Sales Associate}

Assist customers with selection of electronic and computer component and 
tools, consumer and enterprise grade networking equipment based on their needs.

\item{Feburary 2013 -- May 2013}
     {Georgia State University, Atlanta, GA}
     {Teaching Assistant}

Create challange questions to check students comprehension of physics 
concepts. Grading labs, tests and other assignments in a timely manner.

\item{February 2012 -- September 2012}
     {Roswell Telemetry, Roswell, GA}
     {Embedded Systems Programmer and Electrical Engineer}

Port Atmel .Net Micorframework for over the air reprograming. Construct 
and maintain prototyping equipment including an aluminum forge and 3D 
printer. QC and Debug failed hardware. Research materials for future 
improvement of products. Produce and test field electronics.

\item{January 1994 -- June 1996}
     {Seven Diesel s.p.a., Rovato}
     {Engineering department director}

Planning of nozzles for diesel engines and organization of production.
Upgraded the management software by implementing a system for data
handling and automatic drawing generation (in DXF) developed on the
SuperBase 95 RAD tool.

\end{eventlist}

\personal
    [www.entidi.com]
    {viale Conciliazione, 13\newline 25039 -- Travagliato (BS)}
    {+39 (30) 6862332}
    {ntd@entidi.it}

\section{Education}

\begin{yearlist}

\item[High school diploma]{1988 -- 1992}
     {Informatic engineer}
     {ITIS Castelli, Brescia}

\item{1987 -- 1988}
     {Classical gymnasium}
     {Seminario vescovile, Cremona}

\end{yearlist}

\section{Public projects}

\begin{yearlist}

\item{2012}
     {ntdisp (\href{http://ntdisp.entidi.com/}{ntdisp.entidi.com})}
     {Embedded devices programmer}

\item{2007}
     {tip (\href{http://tip.entidi.com/}{tip.entidi.com})}
     {PHP framework based on PEAR}

\item{2006}
     {adg (\href{http://adg.entidi.com/}{adg.entidi.com})}
     {Automatic drawing generation}

\item{2006}
     {gtk2panel (\href{http://gtk2panel.entidi.com/}{gtk2panel.entidi.com})}
     {Top panel menu in GTK+2}

\item{2004}
     {ntd (\href{http://ntd.entidi.com/}{ntd.entidi.com})}
     {General purpose libraries}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Italian}{Native speaker}
\item{English}{Oral: fair -- Written: good}
\item{Spanish}{Oral: good}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Good level}
     {C, PHP, HTML, CSS, autotools, git, gcc, GTK+, GObject, shell,
      MS-DOS, Linux, ladder, G-Code}

\item{Intermediate}
     {Lua, \LaTeX, MySQL, VBA, cuBasic, pascal, subversion, LabVIEW}

\item{Basic level}
     {Windows, FreeBSD, OpenIndiana, Postgres}

\end{factlist}

\end{document}
