%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Sawaiz Syed}{}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:sawaiz.at.sawaizsyed.dot.com}{sawaiz\mbox{}@\mbox{}sawaizsyed.com}\sbull
678-457-2610\sbull
%{sawaiz.syed} \emph{(Skype)}\sbull
%\href{http://www.linkedin.com/in/sawaizsyed}{www.linkedin.com/in/sawaizsyed}
%\\
190 Lembeth Ct.\sbull
Alpharetta\sbull
Gerogia \sbull
30004

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Work Experience}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://phynp6.phy-astr.gsu.edu/~phenix/new/home.html}{Georgia State University, Department of Physics}}
  {\textsc{Atlanta, Georgia}} {%
  \headedsubsection
    {Hardware Developer}
    {January 2014 -- present}
    {\bodytext{Design a low power embedded system mesh to communicate 
    with nodes and provide radiation readings for analysis. CAD layout 
    and electronic design of high voltage and radio communication 
    systems. Design for reducing cost of final product for production. 
    Software development using C, C++. Create documentation for future 
    users and development.}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {\href{http://www.frys.com}{Fry's Electronics}}
  {\textsc{Alpharetta, Georgia}} {%
  \headedsubsection
    {Sales Associate}
    {December 2013 -- February 2014}
    {\bodytext{Assisted customers with selection of electronic and 
    computer component and tools, consumer and enterprise grade 
    networking equipment based on their needs.}}
}

\headedsection
  {\href{http://www.phy-astr.gsu.edu/new_web/index.html}{Georgia State University, Physics Department}}
  {\textsc{Atlanta, Georgia}} {%

  \headedsubsection
    {Teaching Assistant for PHYS-1112K}
    {February 2013 -- May 2013}
    {\bodytext{Created challenge questions to check students' 
    comprehension of physics concepts. Graded labs, tests and other 
    assignments in a timely manner.}}
}

\headedsection
  {\href{http://www.roswelltelemetry.com}{Roswell Telemetry}}
  {\textsc{Roswell, Georgia}} {%
  \headedsubsection
    {Embedded Systems Programmer \& Electrical Engineer}
    {February 2012 -- September 2012}
    {\bodytext{Port Atmel \href{http://www.microsoft.com/net/multiple-platform-support}{.Net Micorframework}
     for over the air reprogramming. Constructed 
	and maintained prototyping equipment including an aluminum forge and a 3D 
	printer. QC and Debug failed hardware. Research materials for future 
	improvement of products. Produced and tested field electronics.}}
}

\headedsection
  {\href{https://www.kroger.com/}{Kroger Company}}
  {\textsc{Alpharetta, Georgia}} {%
  \headedsubsection
    {Courtesy Clerk}
    {June 2010 -- January 2011}
    {\bodytext{Managed front-end supplies and replenished as needed. 
    Maintained clean and safe environment as required by standards.}}
}


\spacedhrule{0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.gsu.edu}{Georgia State University}}
  {\textsc{Atlanta, Georgia}} {%
  \headedsubsection
    {Bachelor of Science, Physics \& Computer Science}
    {Expected Graduation 2015}
    {}
}

\headedsection
  {\href{http://school.fultonschools.org/hs/alpharetta/pages/default.aspx}{Alpharetta High School}}
  {\textsc{Alpharetta, Georgia}} {%
  \headedsubsection
    {Dual Diploma: College Prep \& Engineering}
    {Spring 2011} {}
}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical:}
  {Electronics Design and prototyping, Circuit Design, Soldering, PCB Layout  (\href{http://diptrace.com/}{DipTrace}, \href{http://www.cadsoftusa.com/}{Eagle CAD}), Embedded Systems (\href{http://www.atmel.com/}{Atmel}, \href{http://www.arduino.cc/}{Arduino}), Workstation, server and network management and construction, Robotics, \href{http://en.wikipedia.org/wiki/Numerical_control}{CNC} milling/cutting/printing, Remote Control and autonomous flight, Molding and Casting, Photography and Filmography.
  }
  \vspace{0.5em}
  \inlineheadsection
  {Programming:}
  {C, C++, Java, Python, \acr{XML}, \acr{SQL}, Android SDK, \href{http://en.wikipedia.org/wiki/G-code}{G-Code}, \href{http://www.latex-project.org}{\LaTeX}, \href{http://www.povray.org/}{POV-Ray}, \acr{FTP}, \acr{GIT}, \acr{SVN}.
  }
    \vspace{0.5em}
  \inlineheadsection
  {Software Packages:}
  {\href{http://www.autodesk.com/}{Autodesk Suite}, \href{http://www.adobe.com/}{Adobe Suite}, \href{http://www.cadsoftusa.com/}{Eagle}, \href{http://www.blender.org/}{Blender}, \href{https://www.eclipse.org/}{Eclipse}, \href{http://www.jetbrains.com/idea/}{Intellij IDEA}, \href{http://audacity.sourceforge.net/}{Audacity}, \href{http://www.sketchup.com/}{SketchUp}, \href{http://www.solidworks.com/}{Solidworks} MS Office Suite, \href{http://en.wikipedia.org/wiki/Computer-aided_manufacturing}{CAM}, Linux/Unix.}
  
\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {English, Urdu \emph{(mother tongue)}, French \emph{(elementary level)}}

\spacedhrule{1.6em}{-0.4em}

\roottitle{Achievements}
  {\href{https://www.citiprogram.org/}{\acr{CITI}} Responsible Conduct of Research certification, \acr{AP} Scholar with Distinction (6 Exams), 1\textsuperscript{st} place \href{http://www.gatechfair.org/}{Georgia Technology Fair} in Robotics with \href{http://www.centricsit.com/}{Centrics IT} scholarship (2010).}
  
\spacedhrule{0.2em}{-0.4em}
  
\roottitle{Organizations}
	{Society of Physics Students (Treasurer), Science Olympiad (Lead Engineer), National Science Honor Society, Science Olympiad Judging -- 62 Hours , Recycling Club -- 60 Hours, SPS Tutoring -- 20 Hours}

\spacedhrule{0.2em}{-0.4em}

\roottitle{Relevant Experiences}
{Designing and building wireless 40W laser cutter (85\% complete). Have built, tested, and placed into production three 3D printers (\href{http://reprap.org/wiki/MendelMax}{Mendel Max}, \href{http://reprap.org/wiki/Mendel}{Mendel}, \href{http://reprap.org/wiki/Kossel}{Kossel Mini}). Hardware development for \href{http://reprap.org/wiki/RepRap}{Rep-Rap} project. Setup and manage home networking and media, data, and backup servers hosted on domain.}

\end{document}