\headedsection  % sets the header for the section and includes any subsections
  {\href{http://phynp6.phy-astr.gsu.edu}{Georgia State University, Nuclear Physics Group}}
  {\textsc{Atlanta, Georgia}} {
  \headedsubsection
    {Lead Hardware Developer}
    {January 2014 -- present}
    {\bodytext{Design hardware (EE, layout, and 3D CAD for HV, RF, High-Speed, microcontroller circuits) for manufacture and produce relevant software (web stack and embedded development using C, C++, JS with source control) and documentation. Manage computing recourses (Scientific Linux, Debian, Centos, Arch). Mentor and teach undergraduate physics students at GSU. Manage internal hardware team, and represent group on site at PHENIX, and beamtests.}
    \textbf{Projects}
    \begin{itemize}
      \renewcommand\labelitemi{--}
      \item \emph{\href{https://github.com/Sawaiz/mppcHighVoltage}{MPPC power supply}:}
        Precision high voltage boost converter with SPI control coupled with 24-bit ADC for temperature and bias read-back providing closed loop control.
      \item \emph{\href{https://github.com/Sawaiz/mppcSensor}{MPPC sensor boards}:}
        Small (25mm $\times$ 7mm) high speed (500Mhz-10Ghz) pre-amplifying and mounting assembly. Interfaced with Cat-5 cable providing power, signal, temperature, and test led control.
      \item \emph{\href{https://github.com/Sawaiz/mppcInterface}{MPPC Interface}:}
        Provides power, bias voltage, and other slow control along with high speed signal routing for 8 sensor boards. Multiple boards can be added to a backplane and controlled through a web interface.
      \item \emph{\href{https://github.com/Sawaiz/scintillatorPanel}{Scintillator Panel}:}
        Plastic scintillator sheets milled, and embedded with wavelength shifting fiber optic for improved light collection efficiency.
      \item \emph{\href{https://github.com/Sawaiz/wirelessGeigerCounter}{Wireless Geiger Counter}:}
        IoT based low cost and power data logging Geiger wand based around the ESP-8266. Logs data locally, or transmits to remote database for radiation monitoring and education.
      \item \emph{\href{https://github.com/Sawaiz/modularRICH}{mRICH}:}
        Modular ring imaging Cherenkov detector for the electron ion collider (EIC) project. Provides differentiation between $\pi^\pm$ and $K^\pm$ particles from collisions. Prototype beamtest, Fermilab (April 2016, June 2018).
      \item \emph{\href{https://github.com/Sawaiz/coincidenceCounter}{Coincidence Counter}:}
        High speed (ns) signal readout, replacing KMEC crate modules with embedded systems for cosmic ray detection and logging.
      \item \emph{\href{https://github.com/Sawaiz/modularHodoscope}{Finger Hodoscope}:}
        Finger scintillators with embedded fibers coupled to MPPC sensors providing position and angle of charged particles. Used for cosmic ray measurements, beamtest, muon tomography.
    \end{itemize}
    }
}