\headedsection  % sets the header for the section and includes any subsections
  {\href{http://smartwins.de}{Smart Wins Technologies GmbH}}
  {\textsc{Berlin, DE}} {
  \headedsubsection
    {Chief Technical Officer (Technischer Leiter)}
    {July 2017 -- present}
    {\bodytext{Manage all technical aspects, architected and designed base system in full, implement hardware and firmware. Assisted in technical aspects of algorithm.  Keep digital assets source controlled and manage permissions, identities, and secrets. Manage and mentor technical team and interns. Pitch to possible investors or partners and provide technical and feasibility insight into business decisions.}

    \textbf{Roles}
    \begin{itemize}
      \renewcommand\labelitemi{--}
      \item \emph{Hardware:}
        Design certifiable hardware (EE, layout, RF design and testing 868Mhz/2.4Ghz, 3D CAD for plastic housing) and optimize for production. Organize, manage, and label inventory used for development and small run production. Assemble (SMD to 0402 with and without stencil), test, and package prototype devices.
      \item \emph{Firmware:}
        Write low power firmware for two microcontroller platforms and maintain the codebase. Local hosting and connecting on low power systems and bridging data transfer to Wi-Fi. Gateway that hosts configuration webpage, REST API, and can connect with DHCP and the provided DNS and out to the internet to work on most home networks. Separate firmware for communication with master chip on gateway and a sleepy node on the sensor (CC1310, TI SimpleLink, C++ with tooling in BASH).
      \item \emph{Tooling:}
        Build applications, design test and programing jigs used for production, testing, and development. Plan and document programing and testing procedures for hardware. Test and teach procedure so quality control is maintained. Implement inventory and management system.
      \item \emph{Design:}
        Website, UI, Packaging, Labeling, Housing.
      \item \emph{Frontend:}
        Build device hosted frontend (HTML5/CSS/Vanilla JS) for space and bandwidth limited gateway, tested across browsers. Configure and manage saved networks locally over REST. Manage and provide feedback on AngularJS frontend.
      \item \emph{Backend:}
        Original architecture for MVP designed with transitioned to Serverless for improved scalability and cost reduction. Archival and forwarding applications for data flow. Limited processing power REST backend on microcontroller hosting REST API to low level functions.
      \item \emph{Security:}
        Source controlled cross platform secret store. Manage identity, permissions, and access to resources and accounts.
      \item \emph{Algorithm:}
        Initial data analysis and preliminary algorithm design (CERN ROOT). Probe into additional methodologies for extracting leak data. Manage progress and testing of data analyst. 
      \item \emph{Operations (AWS/IBM Cloud):}
        Manage servers, domains, DNS, and archival. Reduced total AWS costs by 54\% over 1-month period while increasing stability though moving towards serverless architecture.
    \end{itemize}
    }
}

